---
title: "Homework 1"
output: github_document
---

# Problem 1 
  Variable types & coercion
  
```{r hw1part1}
library(tidyverse)

hw_1 = tibble( 
samp = rnorm(10),
gr_0 = samp > 0,
vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j" ),
vec_level = factor(c("high", "medium", "low", "medium", "high", "low", "high", "medium", "high", "low"))
 )

hw_1

mean(pull(hw_1, var = samp))
mean(pull(hw_1, var = gr_0))
mean(pull(hw_1, var = vec_char))
mean(pull(hw_1, var = vec_level))

```

I am able to take the mean of the variable "samp," which is the random sample size of 10 that follows a normal distribution. 
I am also able to take the mean of the variable "gr_0," which is the summ of the variables that are greater than 0. 
I am unable to take the mean for vec_char and vec_level because those are not numeric, instead they are characters.


```{r hw1part2, eval = FALSE, messages = FALSE, warnings = FALSE}

as.numeric(pull(hw_1, gr_0))
as.numeric(pull(hw_1,vec_char))
as.numeric(pull(hw_1, vec_level))
```

The logic and factor variables are able to convert to numeric variables, presumably because they are ordered (true/false, and 3 levels). 
The character variable is not able to convert to numberic because it is not an ordered variable. 
After this conversion, I would be able to calculate the mean of the factor variable but still not the character. 


# Problem 2

### Loading Penguins to the Dataset

```{r inlinecode}

library(tidyverse)

data("penguins", package="palmerpenguins")

```

The penguin data set has the following variables;  `r colnames(penguins)`. It has `r ncol(penguins)` columns and `r nrow(penguins)` rows. 
The mean flipper length is `r mean(penguins$flipper_length_mm,na.rm=TRUE)`



* Penguins Data set

  * The data set has 8 variables 
      * species (character)
      * island (character)
      * bill length in mm (numerical)  
      * bill depth in mm (numerical)
      * flipper length in mm (numerical)
      * body mass in g (numerical)
      * sex (character)
      * year (numerical)
  * There are 344 rows and 8 columns
  * the mean flipper length is 200.9152 mm 

## Problem 2
#### GGPlot


```{r ggplot, warning=FALSE, messages = FALSE}

library(ggplot2)

penguin_ggplot = ggplot(data = penguins, aes (x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguin_ggplot.jpg", plot = penguin_ggplot)

penguin_ggplot

```

Plot of penguin bill length compared to flipper length is shown here: 


